% \chapter*{Acknowledgments}
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
First and foremost, I would like to acknowledge Prof.~Philip Burrows, for his supervision and advice during the complicated journey that culminated in this thesis work. I am also would like to thank CERN and the John Adams Institute for allowing me to work with two of the most prestigious academic institutions in the world.

During my time at CERN I had the extraordinary possibility to work on different projects learning on the field different aspects of the  accelerator physics world. I had the privilege to meet and work alongside some great scientists, while being encouraged to follow and satisfy my scientific curiosity. My deepest gratitude goes to all of you. 

I want to particularly thank Michal Krupa for his constant support. His guidance and supervision was vital for the development and completion of this work with its tight timeline. I also want to thank Manfred Wendt for the supervision and for transmitting his passion for the radio frequency engineering.

My gratitude goes to the Thibaut Lefevre, Stefano Mazzoni and Michele Bergamaschi, and to the colleagues of the AWAKE experiment Anna-Maria Bachmann and Patric Muggli for the discussions and support on the field work. The collaboration of the staff of the CLEAR facility was crucial for a large part of the experimental work, in particular from Antonio Gilardi, Wilfrid Farabolini and Alessandro Curcio.

I also have to thank Dr.~Frank Tecker for supervising me during the first half of my doctoral studies, allowing me to study and practice beam dynamics on the field.

Last, I am grateful to my family and my friends, that sustained me and walked with me a part of this journey.

\end{abstract}